---
title: "Advanced Bioinformatics 2023 Assignment"
author: '1900357'
date: "10/04/2023"
output:
  word_document: default
  html_document: default
---

General RStudio Task 
#create vector 
```{r}
x <-- c(5-55)
```
#sum of all values between 5 and 55
```{r}
sum(x)
```
#
```{r}
nterms = as.integer(readline(prompt="How many terms? "))
```

```{r}
n1=1
n2=1
count=2
```

```{r}
if(nterms <= 0) {
print("Plese enter a positive integer")
} else {
if(nterms == 1) {
print("Fibonacci sequence:")
print(n1)
} else {
print("Fibonacci sequence:")
print(n1)
print(n2)
while(count < nterms) {
nth = n1 + n2
print(nth)
# update values
n1 = n2
n2 = nth
count = count + 1
}
}
}
```
#The "mtcars" dataset is an in-built dataset that provides information in regards to 32 different types of cars. 
```{r}
data(mtcars)
```
#The head() function allows us to see the first 6 rows of the mtcars dataset. 
```{r}
head(mtcars)
```
#We can use different plot functions to visualise the dataset. For instance, the coding chunk below creates a histogram for "mpg" values. The '$' specifies only 'mpg' values, whilst the xlab and ylab give the x- and y-axis correct labels. 
```{r}
hist(mtcars$mpg,
     col='steelblue',
     main='Histogram',
     xlab='mpg',
     ylab='Frequency')
```
#In order to create a ggplot, we must first install the "ggplots2" package into R.
```{r}
install.packages("ggplot2")
```

```{r}
library(ggplot2)
```

```{r}
e <- ggplot(mtcars, aes(x = mpg, y = gear)) +
  geom_bar() 
```

```{r}
e <- ggplot(mtcars, aes(x = mpg, y = gear)) +
  geom_point() 
```

```{r}
e <- 'gglpot_mtcars_dataset'
```

```{r}
plot(mtcars$mpg, mtcars$gear,
     col='magenta',
     main='MPG-GEAR PLOT',
     xlab='mpg',
     ylab='gear',
     pch=19)
```

#The plot() function wil be used to plot a graph of speed against breaking distance.
```{r}
plot(vs ~ disp, data = mtcars, col=2)
```
#Then we are able to use the lm() function, as below:
```{r}
fit <- lm(vs ~ disp, data = mtcars)
```

#This summary() function is one way to view the output. 
```{r}
summary(fit)
```
```{r}
plot(vs ~ disp, data = mtcars, col = 3)
```

```{r}
fit <- lm(mpg ~ wt, data = mtcars)
```

```{r}
require(graphics)
pairs(mtcars, main = "mtcars data", gap = 1/4)
coplot(mpg ~ gear | as.factor(gear), data = mtcars,
       panel = panel.smooth, rows = 1)
```

```{r}
require(graphics)
```

```{r}
plot(vs ~ disp, data = mtcars, col = 6)
```

